### 2019-08-28 README.Rmd
added a talking point
added to talking points
updated to do list

- Paper
    - Can you re-explain your vision with the minipage format?
    - Sometimes LIME doesn't work on my computer anymore...
    - Explain the details of the locality paper to Heike (ask about the radius definition)
- Internship
    - Dixon said he is fine with me switching to 10 hours in the spring (as long as Dr. Caragea agrees)
- Graphics Group
    - show updated schedule
    - email list (should I be added as an admin?)
    - Susan's idea (could we ask Joe, Erin, and/or Charlotte if they would be interested in preparing this talk?)
    - How to include an image in the preview of a post in blogdown?
    - Are you still available to talk next week?

>>>>

- Paper
    - I reorganized my work into three repos and consolidated the journals
    - Can you re-explain your vision with the minipage format?
    - Sometimes LIME doesn't work on my computer anymore...
    - Explain the details of the locality paper to Heike (ask about the radius definition)
    - Should I make the LIME procedure more general?
- Internship
    - Dixon said he is fine with me switching to 10 hours in the spring (as long as Dr. Caragea agrees)
    - See list of activites for Fall 2019
- Graphics Group
    - show updated schedule
    - email list (should I be added as an admin?)
    - Susan's idea (could we ask Joe, Erin, and/or Charlotte if they would be interested in preparing this talk?)
    - How to include an image in the preview of a post in blogdown?
    - Are you still available to talk next week?
    - Cookies for tomorrow?
